---
title: "Beta diversity from hyperspectral remote sensing:"
subtitle: "trading field techs for neural nets?"
author: "Chris Hamm, Max Joseph, & Henry Senyondo"
date: "June 25, 2016"
output:
  beamer_presentation:
    latex_engine: xelatex
    fonttheme: "structurebold"
header-includes: 
- \usepackage{graphicx}
- \beamertemplatenavigationsymbolsempty
- \usefonttheme{professionalfonts}
- \usefonttheme{serif}
- \usepackage{fontspec}
- \usepackage{xcolor}
- \setmainfont{Nimbus Sans L}
- \definecolor{foreground}{RGB}{0,0,0}
- \definecolor{background}{RGB}{255,255,255}
- \definecolor{title}{RGB}{0,120,255}
- \definecolor{gray}{RGB}{155,155,155}
- \definecolor{subtitle}{RGB}{51,204,51}
- \definecolor{hilight}{RGB}{102,255,204}
- \definecolor{vhilight}{RGB}{255,111,207}
- \setbeamercolor{titlelike}{fg=title}
- \setbeamercolor{subtitle}{fg=subtitle}
- \setbeamercolor{institute}{fg=gray}
- \setbeamercolor{normal text}{fg=foreground,bg=background}
- \setbeamercolor{local structure}{fg=title}
- \setbeamertemplate{frametitle}{\begin{centering} \insertframetitle \par \end{centering}}
---

```{r load-helpers, echo=FALSE, message=FALSE, warning=FALSE}

library(raster)
library(rhdf5)
library(rgdal)
library(neonAOP)
library(rgeos)
library(magrittr)

```


# Questions

1. How do in-situ and hyperspectral diversity measurements compare?

2. Can we classify species easily using hyperspectral data?

# Introduction

# Approach

1.

2.

3.


# Data Used and Preprocessing

```{r extracting plot data }

```




# Finding HDF5 files for the hyperspectral data 
```{r}

```

# get extents for each flight hyperspectral raster and each plot
```{r}

```

# get extents for each plot and draw on plot

```{r}


```

# evaluating sampled data

# Results

# conlcusion


# Questions



